Unity in diversity: shared basic social-cognitive processing in children from from 17 diverse communities

### 2024-01-29 paper/supplement.Rmd
prep merge

---
title: "Unity in diversity: Children from 17 communities process gaze in similar ways"
subtitle: "Supplementary material"
author: "..."
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\figurename}{Supplementary Figure}
  \renewcommand{\tablename}{Supplementary Table}
---

```{r, echo=FALSE, message=F}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidyboot)
library(maps)
library(brms)
library(cowplot)
library(ggridges)
library(papaja)

@@

@@

A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study. Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(data$country)` different countries. Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information. Additional children were recruited but did not contribute data to the study. The recruitment strategy varied from community to community and we therefore cannot provide detailed information about the number of children that were excluded. All children who contributed at least five valid data points were included in the final sample. We did not exclude any participants for performance reasons. A detailed description of each site and the way children were recruited can be found below.

@@

```{r figpred1, include = T, fig.align = "center", fig.cap = "Age distribution (left) and prevalence of different types of technology by community. Left: dots show individual data points. Right: color shows the proportion of children with access to screens or touchscreens."}
techpred <- plot_grid(page, ppred, align = "h", rel_widths = c(1, 0.5))

ggsave(plot = techpred, "../visuals/techpred.png", height = 10, width = 10, scale = 1)

@@

@@

Beijing is an inland city and is surrounded by mountains to its west, north and northeast. Mountain areas occupy about 62% of the municipality's total area. The land is characterized by urban and suburban areas, with parks, squares, and historical buildings located mostly in the downtown districts, and flat agricultural land and mountains in the suburban districts. Beijing has a temperate, continental monsoonal climate, characterized by short spring and autumns, hot and rainy summers, and cold and dry winters. Its average annual temperature is 11 to 14oC. The coldest month in Beijing is January, with an average temperature of -9 to -4oC; the hottest month is July, with an average of 25oC. Around 75 percent of its annual precipitation occurs in summer, with the heaviest rainfall in July and August.

@@

Beijing has various types of residential areas, ranging from traditional courtyard houses (siheyuan) in hutongs (narrow alleyways) to modern apartment buildings, gated residential complexes and detached houses. Household composition varies, ranging from single individuals and couples to families with children and multi-generational households. Notably, it is a strong tradition for grandparents to be involved in grandchildren care and household tasks. In big cities, such as Beijing, the involvement of grandparents in grandchild care is especially helpful since it relieves the high-pressure of a two-career family. BTW, China fully implemented the “two-child-per-family” policy in 2016, there are usually one or two children per family now in Beijing.

@@

Children growing up in Beijing have a high exposure to technology. Smartphones and other touchscreen devices are prevalent in most families in Beijing and are used widely for education, communication, and entertainment. In 2022, almost every Chinese netizen accessed the internet via mobile devices and Beijing has been fully covered by ultrafast 5G signals.

@@

The main sectors of the economy in Zambia is agriculture and copper mining and smelting especially in the northern Copperbelt region. Despite these large copper deposits, Zambia is one of the poorest countries in the world. Three quarters of the poor live in rural areas. As in other African countries there is a strong trend of movement from rural arears to urban centers whereby men migrate more often and women remain behind in villages. The housing style in rural areas vary a lot by ethnic group. Overall, mud and thatch, brick, or other materials are used for construction.

@@

The community predominantly practices subsistence farming, cultivating crops like maize, cassava, sweet potatoes, and beans. Wealthier families sometimes keep goats, pigs, chickens, or ducks. Additionally, sugarcane and coffee cultivation contribute significantly to the local economy, with the Kinyara Sugar Company playing a pivotal role in sugarcane harvesting.
Living conditions in the community are characterized by extended families residing together, with an average of 10 people under one roof. While temporary round mud huts are common, permanent houses are found in the trading center of Nyabyeya. Most people in the community live by hand to mouth, and parents (especially women) work hard to provide the basics for their household members.

@@

Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km2  inside the Mexican State. (Ocuilan, n.d.) Geographically Ocuilan has an altitude of between 1000 to 2,600 m situated 80 km south of Mexico City. (INEGI,2010)

@@

dempred <- data%>%
  group_by(community,continent)%>%
  mutate(older_children = children - 1 - younger_children)%>%
  distinct(subjid, .keep_all = T)%>%
  select(subjid, community, continent, older_children,children, younger_children, household)%>%
  pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
  mutate(dem = recode(dem,
                      older_children = "older children",
                            younger_children = "younger children"),
         dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
  ggplot(aes(y = community, x = value))+
  facet_grid(continent~dem, scales = "free", space = "free_y")+
  geom_density_ridges(
    jittered_points = TRUE,
    position = position_points_jitter(width = 0.25, height = 0),
    point_shape = '|',  point_alpha = 1, alpha = 0.7,
  )+
 # geom_density_ridges(
 #    col = "white",
 #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
 #    vline_size = 1, vline_color = "red",
 #    point_size = 0.4, point_alpha = 1,
 #    position = position_raincloud(adjust_vlines = TRUE)
 #  )
  labs(x = "No. of individuals", y= "")+
  #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
  theme_few()

ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)

@@

```{r figagents, include = T, fig.align = "center", fig.cap = "Screenshot from the task. The scene depicts the choice phase in a test trial. Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
knitr::include_graphics("../visuals/task.png")
```

There were two types of familiarization trials. In fam1 trials, the balloon fell down and landed in plain sight. Participants simply had to touch the visible balloon. In fam2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (usually a hedge - see Figure XXB). Thus, participants needed to touch the hedge where they saw the balloon land. Next came test trials. Here, the barrier moved up and covered the balloons trajectory. That is, participants only saw the agents eyes move, but not the balloon. They had to infer the location of the balloon based on the agent's gaze direction. During fam1, fam2 and the first test trial, children heard voice overs commenting what happened on the screen. Critically, the agent was described as wanting to help the child and to always look at the balloon (see section [script](#appendix-script) for the English wording).

@@

>>>>

---
title: "Unity in diversity: shared basic social-cognitive processing in children from from 17 diverse communities"
subtitle: "Supplementary material"
author: "..."
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\figurename}{Supplementary Figure}
  \renewcommand{\tablename}{Supplementary Table}
---

```{r, echo=FALSE, message=F}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(ggpubr)
library(tidyboot)
library(tidybayes)
library(maps)
library(brms)
library(cowplot)
library(ggridges)
library(papaja)
library(coda)
library(ggrepel)

@@

set.seed(1337)
```

@@

@@

```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community. Left: dots show individual data points. Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))

ggsave(plot = techpred, "../visuals/techpred.png",  height = 7, width = 10, scale = 1)

@@

A total of `r sum(as.numeric(demtab$N))` children between `r round(min(data$ageinyears), 2)` and `r round(max(data$ageinyears), 2)` provided data for the study. Children lived in `r n_distinct(data$community)` different communities, located in `r n_distinct(data$country)` different countries. Table \@ref(tab:demtable) gives the sample size per community together with some basic demographic information. Figure \@ref(fig:figpred1)A shows the age distribution in each setting. Additional children were recruited but did not contribute data to the study. The recruitment strategy varied from community to community and we therefore cannot provide detailed information about the number of children that were excluded. All children who contributed at least four valid data points were included in the final sample. We did not exclude any participants for performance reasons. A detailed description of each site and the way children were recruited can be found below.

@@

Beijing is an inland city and is surrounded by mountains to its west, north and northeast. Mountain areas occupy about 62% of the municipality's total area. The land is characterized by urban and suburban areas, with parks, squares, and historical buildings located mostly in the downtown districts, and flat agricultural land and mountains in the suburban districts. Beijing has a temperate, continental monsoonal climate, characterized by short spring and autumns, hot and rainy summers, and cold and dry winters. Its average annual temperature is 11 to 14oC. The coldest month in Beijing is January, with an average temperature of -9 to -4°C; the hottest month is July, with an average of 25°C. Around 75 percent of its annual precipitation occurs in summer, with the heaviest rainfall in July and August.

@@

Beijing has various types of residential areas, ranging from traditional courtyard houses (siheyuan) in hutongs (narrow alleyways) to modern apartment buildings, gated residential complexes and detached houses. Household composition varies, ranging from single individuals and couples to families with children and multi-generational households. Notably, it is a strong tradition for grandparents to be involved in grandchildren care and household tasks. In big cities, such as Beijing, the involvement of grandparents in grandchild care is especially helpful since it relieves the high-pressure of a two-career family. Since China fully implemented the “two-child-per-family” policy in 2016, there are now usually one or two children per family in Beijing.

@@

Children growing up in Beijing have a high exposure to technology. Smartphones and other touchscreen devices are prevalent in most families in Beijing and are used widely for education, communication, and entertainment. In 2022, almost every Chinese citizen accessed the internet via mobile devices and Beijing has been fully covered by ultra fast 5G signals.

@@

The main sectors of the economy in Zambia is agriculture and copper mining and smelting especially in the northern Copperbelt region. Despite these large copper deposits, Zambia is one of the poorest countries in the world. Three quarters of the poor live in rural areas. As in other African countries there is a strong trend of movement from rural areas to urban centers whereby men migrate more often and women remain behind in villages. The housing style in rural areas vary a lot by ethnic group. Overall, mud and thatch, brick, or other materials are used for construction.

@@

The community predominantly practices subsistence farming, cultivating crops like maize, cassava, sweet potatoes, and beans. Wealthier families sometimes keep goats, pigs, chickens, or ducks. Additionally, sugarcane and coffee cultivation contribute significantly to the local economy, with the Kinyara Sugar Company playing a pivotal role in sugarcane harvesting.

Living conditions in the community are characterized by extended families residing together, with an average of 10 people under one roof. While temporary round mud huts are common, permanent houses are found in the trading center of Nyabyeya. Most people in the community live by hand to mouth, and parents (especially women) work hard to provide the basics for their household members.

@@

Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km2  inside the Mexican State (Ocuilan, n.d.). Geographically Ocuilan has an altitude of between 1000 to 2,600 m situated 80 km south of Mexico City. (INEGI,2010)

@@

# dempred <- data%>%
#   group_by(community,continent)%>%
#   mutate(older_children = children - 1 - younger_children)%>%
#   distinct(subjid, .keep_all = T)%>%
#   select(subjid, community, continent, older_children,children, younger_children, household)%>%
#   pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
#   mutate(dem = recode(dem,
#                       older_children = "older children",
#                             younger_children = "younger children"),
#          dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
#   ggplot(aes(y = community, x = value))+
#   facet_grid(continent~dem, scales = "free", space = "free_y")+
#   geom_density_ridges(
#     jittered_points = TRUE,
#     position = position_points_jitter(width = 0.25, height = 0),
#     point_shape = '|',  point_alpha = 1, alpha = 0.7,
#   )+
#  # geom_density_ridges(
#  #    col = "white",
#  #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
#  #    vline_size = 1, vline_color = "red",
#  #    point_size = 0.4, point_alpha = 1,
#  #    position = position_raincloud(adjust_vlines = TRUE)
#  #  )
#   labs(x = "No. of individuals", y= "")+
#   #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
#   theme_few()
# 
# ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)

@@

```{r figtask, include = T, fig.align = "center", fig.cap = "Screenshot from the task. The scene depicts the choice phase in a test trial. Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
knitr::include_graphics("../visuals/task.png")
```

There were two types of familiarization trials. In fam1 trials, the balloon fell down and landed in plain sight. Participants simply had to touch the visible balloon. In fam2 trials, the trajectory of the balloon was visible but it landed behind a small barrier (usually a hedge - see Figure \@ref(fig:task)). Thus, participants needed to touch the hedge where they saw the balloon land. Next came test trials. Here, the barrier moved up and covered the balloons trajectory. That is, participants only saw the agents eyes move, but not the balloon. They had to infer the location of the balloon based on the agent's gaze direction. During fam1, fam2 and the first test trial, children heard voice overs commenting what happened on the screen. Critically, the agent was described as wanting to help the child and to always look at the balloon (see section [script](#appendix-script) for the English wording).

@@

We analysed the data in three steps. First, we tested whether there was substantial cross-cultural variation in performance. Second, we looked for signatures in the data that informed the hypothesis that children processed gaze in the same way across cultural settings. Finally, we related performance in the task (on an individual level) to aspects of everyday experience, in particular the exposure to screen-based technology and social interaction (approximated by household composition).

We used Bayesian Regression models fit in `R` [] using the package `brms` [@burkner2019bayesian] for all analyses except the cognitive models, which were implemented in the probabilistic programming language `webppl` [@dippl]. For regression models, we used the default priors built in to `brms`. The dependent variable in all regression models was imprecision, that is, the absolute distance between the true location of the balloon (to x-coordinate of its center) and the location where the participant touched the screen. We used a Log-normal distribution to model the data because the natural lower bound for imprecision is zero and the data was right skewed with a long tail to the right. Numeric predictors that entered the models were scaled to have a mean of zero and a standard deviation of 1. For each model we ran four chains with 6000 iterations, removing the first 2000 for burn-in. All models had converging chains (Rhat values < 1.01). Details specific to each analysis can be found below. The analysis code can be found in the online repository associated with the study (link).

We pre-registered an analysis plan at https://osf.io/tdsvc. The analyses reported below follow the same logical as the pre-registered analyses but they differ substantially in detail. The main difference lies in the random effects structure we used in the models. In the pre-registration, we did not include random slopes for target centrality (i.e. the distance of the location where the balloon landed from the center of the screen), neither within subject nor within cultural setting. Instead, we included random slopes for trial within subject. We decided to change this and remove random slopes for trial but include them for target centrality. The reasons were as follows: trail effects in the sense of learning across trials were unlikely because participants did not receive differential feedback. Furthermore, in multiple studies with the same task since the registration we never found any trial effects [@prein2023tango; @prein2023variation]. We therefore removed trial from the models completely to reduce model complexity. On the other hand, we included random slopes for target centrality to be able to look at cross-cultural variation. The cognitive model was not mentioned in the pre-registration because it is a more recent development [see @prein2023variation].

## Cross-cultural variation

As a first step, we investigated cross-cultural variation in performance. As stated in the pre-registration, this can be problematic when including random intercepts for participant and cultural setting at the same time. Participants are fully nested within cultural setting. If there was an effect of cultural setting, we would expect participant random intercepts to cluster by cultural setting. This clustering would appear whether or not cultural setting would be included in the model as a random effect or not -- the only difference would be if the participant random intercepts are estimated as a deviation from a grand intercept or a culture-specific one. Standard metrics such as `WAIC` or `LOO` would penalize the model with additional intercept for cultural setting for having additional parameters that do not help to improve predictive accuracy.

To get around this problem, we used a cross-validation procedure [see e.g., @stengelin2023children]. For each cultural setting we randomly sampled a data set that was 5/6 the size of the full data set (training data). Then we fit the model to this training data and used the estimated model parameters to predict the remaining 1/6 of the data (testing data). We then compared the model predictions from the different models by computing the mean difference between the true and predicted imprecision, over all trials in the testing data set. This approach gets around the problem mentioned in above because the model predicts a new dataset for which the individual random intercepts are unknown. Clustering by culture could therefore only be predicted by a model that included culture as a predictor. We repeated the cross-validation procedure 100 times and counted which model performed best most often.

We compared the following models (`brms` notation):

`null`:
* `imprecision ~ age + target_centrality + (target_centrality | participant)`

`culture`:
* `imprecision ~ age + target_centrality + (target_centrality | participant) + (target_centrality | culture)`

`culture_age`: 
* `imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | culture)`

```{r}
mdata <- data%>%
  ungroup()%>%
  mutate(older_children = children - 1 - younger_children)%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         touchscreen = factor(touchscreen),
         screen = factor(screen),
         click = abs(clickdistfromtargetcenterx))
```

```{r}
bm_null <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid),
                              data   = mdata,
                              family = lognormal(),
                              warmup = 2000,
                              iter   = 6000,
                              chains = 4,
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

saveRDS(bm_null, "../saves/bm_cv_null.rds")

bm_cult <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid)+ (1 |community),
                              data   = mdata,
                              family = lognormal(),
                              warmup = 2000,
                              iter   = 6000,
                              chains = 4,
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

saveRDS(bm_cult, "../saves/bm_cv_cult.rds")

bm_cult_age <- brm(click ~ ageinyears + targetcentralityx + (trialnr + targetcentralityx|subjid)+ (ageinyears + targetcentralityx |community),
                              data   = mdata,
                              family = lognormal(),
                              warmup = 2000,
                              iter   = 6000,
                              chains = 4,
                              cores  = 4,
                              threads = threading(8),
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")

saveRDS(bm_cult_age, "../saves/bm_cv_cult_age.rds")

fixef(bm_cult_age)%>%as_tibble(rownames = "term")%>%mutate_if(is.numeric, round, 2)%>%saveRDS(.,"../saves/cult_age_fix.rds")

```{r}
six_fold_cross_validation <- function(data, m1, m2, m3, m4, repeats) {

  N_ids = n_distinct(data$subjid)
#Prepare results DF
  results <- tibble(
    m1_score=numeric(), 
    m2_score=numeric(), 
    m3_score=numeric(), 
    #m4_score=numeric(),

    #m4_beats_m3=logical(), 
    #m4_beats_m2=logical(), 
    #m4_beats_m1=logical(), 
    m3_beats_m2=logical(), 
    m3_beats_m1=logical(), 
    m2_beats_m1=logical(),

    m1 = character(), 
    m2 = character(), 
    m3 = character(),
    #m4 = character()
    )

#Repeat the whole shebang several times
  for(i in 1:repeats) {

  # Split dataset into 6 bins
  bin_data <- data%>%distinct(community, subjid)%>%group_by(community) %>% mutate(bin = rep(1:6, length.out = n()))

for(j in 1:6) {
    # Use bin j as "hold out" data
    testing_ids <- bin_data%>%filter(bin == j)%>%pull(subjid)
    training_ids <- bin_data%>%filter(bin != j)%>%pull(subjid)
    # Safety check - is partition complete and disjoint?
    stopifnot(length(testing_ids) + length(training_ids) == N_ids)
    stopifnot(length(intersect(testing_ids, training_ids)) == 0)
# Create two separate dataframes
    testing_data <- filter(data, subjid %in% testing_ids)
    training_data <- filter(data, subjid %in% training_ids)

    # Train models
    up_m1 <- update(m1, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
    up_m2 <- update(m2, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
    up_m3 <- update(m3, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))
    #up_m4 <- update(m4, newdata=training_data, cores=4,backend = "cmdstanr", threads = threading(8))

    # Sample predictions
    preds_m1 <- posterior_predict(up_m1, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    preds_m2 <- posterior_predict(up_m2, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    preds_m3 <- posterior_predict(up_m3, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")
    #preds_m4 <- posterior_predict(up_m4, newdata=testing_data, allow_new_levels=TRUE, sample_new_levels="gaussian")

    # Evaluate predictive accuracy
  score_m1 <- mean(sqrt(colMeans((testing_data$click - t(preds_m1))**2)))
  score_m2 <- mean(sqrt(colMeans((testing_data$click - t(preds_m2))**2)))
  score_m3 <- mean(sqrt(colMeans((testing_data$click - t(preds_m3))**2)))
  #score_m4 <- mean(sqrt(colMeans((testing_data$click - t(preds_m4))**2)))

  m1_name <-  as.character(substitute(m1))
  m2_name <-  as.character(substitute(m2))
  m3_name <-  as.character(substitute(m3))
  #m4_name <-  as.character(substitute(m4))

    # Record results
    results <- add_row(results,

                       repeats = i, 
                       bin = j,

                       m1_score = score_m1,
                       m2_score = score_m2,
                       m3_score = score_m3,
                       #m4_score = score_m4,

                       # m4_beats_m3 = m4_score < m3_score,
                       # m4_beats_m2 = m4_score < m2_score,
                       # m4_beats_m2 = m4_score < m1_score,
                       m3_beats_m2 = m3_score < m2_score,
                       m3_beats_m1 = m3_score < m1_score,
                       m2_beats_m1 = m2_score < m1_score,

                       m1  = m1_name,
                       m2 = m2_name,
                       m3 = m3_name,
                       #m4 = m4_name
                       )
 }
  }
  return(results)
}
```

```{r}
cv_cult <- six_fold_cross_validation(scdata, bm_base, bm_cult, bm_cult_age, 1)
```

We pre-registered the inclusion of additional models which did not include age as a predictor. To reduce computational demands and given that we did not implement this approach to determine the effect of age, we decided to leave these models out so that all models included age as a predictor. The main questions were, therefore, whether there were systematic absolute (model `culture`) or also developmental (model `culture_age`) differences between cultural settings.

The results showed that the `culture_age` model made, by far, the best predictions and outperformed the `culture` model in `r mean(cv_cult$m3_beats_m2)*100`% and the `null` model in `r mean(cv_cult$m3_beats_m1)*100`% of cases. Furthermore, the `culture` model outperformed the `null` model in `r mean(cv_cult$m2_beats_m1)*100` % of cases. This suggests that there were substantial absolute and developmental differences between cultural settings (see Figure \@ref(fig:figdev)A).

## Processing signatures

In the second analysis focused on signatures in the data that suggest that children in all cultural settings use similar cognitive processes to infer the location of the balloon. The first -- weaker -- signature was simply an increase in performance with age. The second -- stronger -- signature was a strong effect of target centrality. That is, the further away from the center the balloon lands, the more imprecise should participants be. This second signature is derived from the model by the cognitive model introduced in @prein2023variation. It predicts that trials in which the agent looks further away from the center (i.e. to the left or right side of the screen) result in higher levels of imprecision compared to trials in which the agent looks closer to the middle.

This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface. The width of the light beam represents each individual's level of uncertainty in vector estimation and is represented in the model as a normal distribution around the true gaze vector with a participant specific standard deviation. On each trial, the model assumes that the participant samples a vector from this distribution to infer the location of the balloon. The smaller the standard deviation -- -- the narrower the light beam --, the more precise on average the participant is. Now, when the torch is directed straight down, the light beam is concentrated in a relatively small area. When the torch is rotated to the side, the the light from one half of the cone must travel further than the light from the other half to reach the surface. As a consequence, the light is spread over a wider area. This is true no matter how wide the cone (how large the standard deviation) is.

```{r}
draws <- bind_rows(
as_draws_df(bm_cult_age)%>%
  select(contains("ageinyears"))%>%
  select(contains("ageinyears"))%>%
  select(-contains("sd"))%>%
  select(-contains("cor"))%>%
  pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_ageinyears,
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",ageinyears]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "ageinyears"),

as_draws_df(bm_cult_age)%>%
  select(contains("targetcentralityx"))%>%
  select(contains("targetcentralityx"))%>%
  select(-contains("sd"))%>%
  select(-contains("cor"))%>%
  select(-contains("subjid"))%>%
  pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
  mutate(post = value + b_targetcentralityx,
         community = str_remove(community, "r_community"),
         community = str_remove(community, ",targetcentralityx]"),
         community = str_remove(community, "\\["))%>%
  select(community, post)%>%
  mutate(type = "targetcentrality")
)%>%
  mutate(community = str_replace(community, "\\.", " "),
         community= str_remove(site,"\\."))

pdraws <- draws%>%
  mutate(community = recode(community, 
                            "Auckland (NewZealand)" = "Auckland (New Zealand)",
                            "BaYaka (Rep.Congo)" = "BaYaka (Rep. Congo)",
                            "Bandongo (Rep.Congo)" = "Bandongo (Rep. Congo)",
                            "Buenos Aires(Argentina)" = "Buenos Aires (Argentina)"))%>%
  left_join(data%>%distinct(community, continent))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))

saveRDS(pdraws, "../saves/pdraws.rds")

post_agg <- pdraws%>%
  group_by(community, type)%>%
  summarise(mean = mean(post),
            lci = hdi_lower(post),
            uci = hdi_upper(post))

saveRDS(post_agg, "../saves/post_agg.rds")
```

```{r figpreds, include = T, fig.align = "center", fig.cap = "Posterior distributions of model estimates for the poredictor variables by cultural setting.", out.width="100%"}

pdraws <- readRDS("../saves/pdraws.rds")%>%
  mutate(type = recode(type,
                       ageinyears = "Age",
                       targetcentrality = "Target centrality"),
         type = factor(type, levels = c("Age","Target centrality")))

ppred <- ggplot(pdraws, aes(x= post, y = community))+

  geom_density_ridges(col = "white", alpha = .75, fill = "grey")+
  geom_vline(xintercept = 0, lty = 3)+
  facet_grid(continent~type, scales = "free", space = "free_y")+
  #stat_pointinterval(size = 0.1)+
  #xlim(-0.15, 0.1)+
  labs(x = "Posterior model estimate", y= "")+
  theme_few()+
  theme( strip.text.y.right = element_text(angle = 0))

ggsave(plot = ppred, "../visuals/pred.png", height = 6, width = 12, scale = 1)

knitr::include_graphics("../visuals/pred.png")

To test these predictions, we inspected the parameter estimates for age and target centrality in the "winning" `culture_age` model described in the previous sections. We found strong main effects of age ($\beta$ = ) and target centrality ($\beta$ =). Figure \@ref(fig:figpreds) visualizes the posterior distributions for each cultural setting and shows that -- despite variation in strength -- there was a strong effect of age and target centrality in all cultural settings.

Another way to look at these signatures is to visualize the group-level developmental trajectories and the aggregated performance at different areas of the screen. Figure \@ref(fig:figdev)A shows that children got more precise with age in all cultural settings. Figure \@ref(fig:figdev)B shows the expected u-shaped pattern: the closer the balloon lands to the center of the screen (bins 5 and 6) the more precise children are in all cultural settings.

```{r}
devdata <- data%>%
  mutate(click = abs(clickdistfromtargetcenterx))%>%
  group_by(subjid, continent,community, ageinyears)%>%
  summarise(mean_click = mean(click))%>%
  ungroup()%>%
  mutate(ageinyears = ageinyears - min(ageinyears))

bm_dev <- brm(mean_click ~ ageinyears + (ageinyears |community),
                              data   = devdata,
                              family = lognormal(),
                              warmup = 2000,
                              iter   = 4000,
                              chains = 4,
                              cores  = 4,
             control = list(adapt_delta = 0.95))

ndata <- devdata%>%
  distinct(continent, community, ageinyears)

post <- fitted(bm_dev, newdata = ndata, re_formula =~(ageinyears|community))%>%
  as_tibble() %>%
  bind_cols(ndata)%>%
  mutate(ageinyears = ageinyears + min(data$ageinyears))
```

```{r}
tc_agg_data<- data%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(continent, community, targetposition)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

tam <- tc_agg_data%>%
  filter(continent == "America")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

taf <- tc_agg_data%>%
  filter(continent == "Africa")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

teu <- tc_agg_data%>%
  filter(continent == "Europe")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

tas <- tc_agg_data%>%
  filter(continent == "Asia")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

toc <- tc_agg_data%>%
  filter(continent == "Oceania")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "Target position (binned)", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

```{r}
am <- ggplot()+
  geom_point(data = mdata%>%filter(continent == "America"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "America"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="Imprecision")+
  scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

af <- ggplot()+
  geom_point(data = mdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

eu <- ggplot()+
  geom_point(data = mdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

as <- ggplot()+
  geom_point(data = mdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
